---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# edx.capstone.movielens.data

<!-- badges: start -->
<!-- badges: end -->

The goal of `edx.capstone.movielens.data`  is to provide the following datasets derived from the  [10M version of the MovieLens Dataset](http://grouplens.org/datasets/movielens/10m/) to use in the _**MovieLens**_ project of the [edX HarvardX PH125.9x Data Science Capstone Course](https://pll.harvard.edu/course/data-science-capstone) for building a _Movie Recommendation System_ according to the course requirements:

* **edx:** use it to develop and train your algorithms;
* **final_holdout_test:** according to the requirements of the course, use it exclusively to evaluate the _**RMSE**_ of your final algorithm.


## Installation

The development version of the package can be installed from _GitHub_ using the `R` programming language with the following line of code:

``` r
# install.packages("pak")
pak::pak("AzKurban-edX-DS/edx.capstone.movielens.data")
```

## Example

Below is a simple example showing how to get an idea of the structure of the datasets included in a package:

```{r example}
library(edx.capstone.movielens.data)
str(edx)
head(edx)

str(final_holdout_test)
head(final_holdout_test)
```

